%% Copyright (C) 2008 Johan Oudinet <oudinet@lri.fr>
%%
%% Permission is granted to make and distribute verbatim copies of
%% this manual provided the copyright notice and this permission notice
%% are preserved on all copies.
%%
%% Permission is granted to process this file through TeX and print the
%% results, provided the printed document carries copying permission
%% notice identical to this one except for the removal of this paragraph
%% (this paragraph not being relevant to the printed manual).
%%
%% Permission is granted to copy and distribute modified versions of this
%% manual under the conditions for verbatim copying, provided that the
%% entire resulting derived work is distributed under the terms of a
%% permission notice identical to this one.
%%
%% Permission is granted to copy and distribute translations of this manual
%% into another language, under the above conditions for modified versions,
%% except that this permission notice may be stated in a translation
%% approved by the Free Software Foundation
%%
\chapter{Introduction to Company and Team}
\label{sec:intro}

\section{Introduction to Company}
\label{sec:isauriam}

Founded in October 2011, Megvii is an Articial Intelligence company specialized in providing enterprises and developers with intelligent solutions and data services,
and is dedicated to the mission of “Create machines that can see and think”.
With the "cloud + end" system of Megvii Cloud and Megvii SensorNet as its core products, Mevgii has successfully offered solutions for over 800 enterprises in nance, security,
office, real estate and other business sectors.

Megvii holds more than 350 domestic and international patents. Over seven years of development, Megvii has gathered a workforce of over 1000 people, among whom more than 70\% are R&D stas. The core team of Megvii is composed of top geeks
who are alumni of universities like Tsinghua, Columbia, Oxford, etc., and adventurers formerly working for Google, Alibaba, Huawei and IBM.
Over 80 people in Megvii have been awarded golden prizes of informatics at national and international levels.
Research teams from Megvii have been and are holding the first places in more than ten international AI benchmarks.

The name ’Megvii’ is from mega vision, which means our work is concentrated on offering computer vision technologies that enable your applications to read and
understand the world better.
In fact, FACE++, the best product of megvii, now, is the biggest platform of face detection over the world.

Here is the link to official website: https://www.faceplusplus.com/


\section{Introduction to Team}
\label{sec:isauriam}

During the internship, I worked in Detection Team in Megvii Research.
The team leader is Gang YU\footnote{His google scholar is: https://scholar.google.com/citations?user=BJdigYsAAAAJ&hl=en}.

In general, our team is in charge of 4 main issues:
\begin{enumerate}
  \item{\textbf{Detection: }} Face Detection, Pedestrian/human Detection, Vehicle/Plate Detection, General Object Detection, Object Detection in Video, 3D Object detection (combined with Point Cloud)
  \item{\textbf{Segmentation: }} Semantic Segmentation, Instance Segmentation, Panoptic Segmentation, Video Segmentation, 3D Segmentation
  \item{\textbf{Skeleton: }} Human Pose Estimation, Hand Pose Estimation
  \item{\textbf{Action: }} Action Recognition in Video
\end{enumerate}

Our team has a solid technical accumulation, especially in the detection aspect. We have the winner solution of COCO2017 Detection:  MegDet\cite{peng2018megdet}.
From a product perspective, we built a small repo of imagenet base model for training and exploring models with less than 100M FLOPs.
In addition to Detection, our skeleton solution also took the first in the COCO2017 Human Pose competition: CPN\cite{chen2017cascaded}.
In terms of Segmentation, we also have some better work published. In addition, we have sufficient GPU resources, as well as very large internal data sets for exploring the upper-bound of various research tasks.




%%% Local Variables:
%%% mode: latex
%%% TeX-master: "rapportM2R"
%%% End:
